Chemical composition analysis for X-ray transport container scans.

### 2018-10-05 EMIN-2018/presentation/main.tex
save

            \includegraphics[width=1\textwidth]{figures/sim_2.jpeg}
        \end{column}
    \end{columns}  
\end{frame}
%-------------Моделирование, часть 2 --------------------------
    \begin{frame}
    \frametitle{Simulation: Thickness reconstruction}
    \begin{columns}
        %        \begin{column}{0.4\textwidth}
        %            \begin{itemize}
        %                \item 
        %                \item 
        %                \item 
        %                
        %            \end{itemize}
        %        \end{column}
        \begin{column}{1\textwidth} 
            \includegraphics[width=1\textwidth]{figures/yed_schema_2.pdf}
        \end{column}
    \end{columns}  
\end{frame}

    \begin{frame}
        %3d -томография
    \frametitle{Simulation: Perspectives}
    \begin{columns}
                \begin{column}{0.6\textwidth}
                    \begin{itemize}
                        \item 
                        \item 
                        \item

                    \end{itemize}
                \end{column}
    \end{columns}  
\end{frame}

@@

    \begin{block}{Results}<1->
%          Измерение спектра фотонов после прохождения контейнера позволяет
%        идентифицировать в контейнере отдельные группы элементов по Z (легкие,
%        средние, тяжелые) в одной экспозиции при одной фиксированной энергии
%        электронов, оптимально вблизи 8 МэВ.     
    \begin{enumerate}
        \item%<1-> Measurement of gamma ray spectrum allow recognize ...
        \item%<2-> 
    \end{enumerate}
    \end{block}
\begin{block}{Plans and perspectives}%<3->
    \begin{enumerate}
        \item%<1-> Measurement of gamma ray spectrum allow recognize ...
        \item%<2-> 
    \end{enumerate}
%   - получить объемные изображения объектов путем облучения контейнера под
%   углом 45 градусов.
%   
%   - разработать программу обработки изображений для автоматического
%   определения соответствия содержимого контейнера заявленной декларации о
%   содержании груза.
%   
%   - провести измерения на ускорителе ЛУЭ-8 в условиях, близким к реальным
%   условиям просвечивания контейнеров (скорость движения, и т.д.).
\end{block}

>>>>

            \includegraphics[width=1\textwidth]{figures/sim_2.jpeg}
        \end{column}
    \end{columns}  
\end{frame}
%-------------Моделирование, часть 2 --------------------------
    \begin{frame}
    \frametitle{Simulation: Thickness reconstruction for one dimensional}
    \begin{columns}
        \begin{column}{0.4\textwidth}
            \begin{block}{Simple model}
                Attenuation of gamma ray flux define as:
                                        $$
                \frac{N(E)}{N_0(E)} = \exp(-\sum_i \Sigma^{mean}_i(E)x_i)
                $$
                where $x_i$ --- thickness of $i$-layer, $\Sigma^{mean}_i$ --- mean cross-section for group of material, $N,~N_0$ - number of gamma.
                \begin{itemize}
                    \item Disregard secondary scattering.
                    \item Disregard annihilation line.
                \end{itemize}

        \end{column}
        \begin{column}{0.55\textwidth}
                  \includegraphics[width=1\textwidth]{figures/yed_schema_2.pdf}
                \begin{block}{Reconstruction algorithm}
                    \begin{itemize}
                        \item Full thickness is known.
                        \item Find thickness using least squares:

                    \end{itemize}
                    $$
                    \sum_E(\ln \frac{N(E)}{N_0(E)} + \sum_i \Sigma^{mean}_i(E)x_i))^2 \to min
                    $$
                \end{block}

        \end{column}
    \end{columns}  
\end{frame}
 \begin{frame}
\frametitle{Simulation: Thickness reconstruction for  one dimensional}
\begin{columns}
            \begin{column}{0.4\textwidth}
                \begin{itemize}
                    \item Used Aluminium, Iron and Lead.
                    \item Several sets of thickness with full thickness from 30 cm to 180 cm.
                    \item Energy resolution of detector is 10 \%

                \end{itemize}
            \end{column}
    \begin{column}{0.7\textwidth} 
        \includegraphics[width=1\textwidth]{figures/relError.pdf}
    \end{column}
\end{columns}  
\end{frame}

    \begin{frame}
        %3d -томография
    \frametitle{Simulation: Perspectives}
    \begin{columns}
                \begin{column}{1\textwidth}
                    \begin{itemize}
                        \item If we will use energy-space distribution we can develop algorithm for \textbf{3D-tomography}

                    \end{itemize}

                \includegraphics[width=1\textwidth]{figures/yed_schema_2.pdf}

            \end{column}
    \end{columns}  
\end{frame}

@@

    \begin{block}{Results}%<1->   
    \begin{enumerate}
        \item Measurement of gamma ray spectrum allow to identify cargo belonging to group with certain $Z_{eff}$ 
        \item Also its allow to define thickness of layers from different element with accuracy about 25\% 
        \item Studied energy resolution of detector based on BGO scintillator, for photodetector with full array of pixel expected energy resolution about 10\%
    \end{enumerate}
    \end{block}
\begin{block}{Plans and perspectives}%<3->
    With financial support can be developed:
    \begin{enumerate}
        \item Program which check cargo of transport container   for compliance cargo manifest
        \item Algorithm for 3D gamma-tomography.
    \end{enumerate}
\end{block}
